\section*{The Penguin Lab}


\subsection*{The Linux Servers}
Penguin
    ``Penguin'' is the Penguin Lab's portal to the outside world.  Students accessing the network from home will initially end within its inner workings.

    Dell PowerEdge 2950
    2x  Intel Xeon 4-Core CPU @2.00 GHz
    8GB RAM

Mumble
    Mumble is the Penguin Lab's http server.  Until recently (2012), the Penguin website, ssh, NFS, and user authentication was all hosted on the Penguin server listed above.  After obtaining two new machines, the system administrators decided it was time to segregate the fundamental activities of the lab; and thus, Mumble was born to initally run Apache and Tomcat together to 
    
    Dell PowerEdge 2650
    Intel Xeon 4-Core CPU @3.06 GHz
    3GB RAM

Auk
    Auk serves as the Penguin Network's user authentication server.

    Dell PowerVault NX300
    Intel Xeon 4-Core CPU @3.40 GHz
    13 GB RAM

Feathers
    Feathers provides the home directory filesystem for the Penguin Network.

    Dell PowerEdge 2850
    Intel Xeon 6-Core CPU @2.143 GHz
    6GB RAM
    6x  1TB HDD's

Happyfeet
    The only remaining 32-bit machine on the Penguin Network, Happyfeet serves as a sandbox for students in the Computer Science department. 

    Dell PowerEdge Model 1750
    %TODO
    Some random circuit boards that were once found lying outside in a dumpster.

\subsection*{Akeley 204 - The Linux Lab}
Sir Oswald Cobblepot
    ``The Penguin,'' as he is known in the DC Comic universe, is Lock Haven's local 'super computer.'  Sporting two nVidia Tesla GPGPU's and an nVidia Quadro FX, it is truly a monocle wearing, umbrella toting master mind.

    Custom Built by Colfax
    Intel Core i7 4-Core CPU @3.2 GHz with Hyper Threading
    2x  nVidia Tesla C1060
        240 General Purpose GPU Cores @1.296 GHz
        4GB Dedicated Memory
    nVidia Quadro FX4800
        190 GPU Cores
        1GB Video RAM
    12GB RAM
        
Waimanu
    A challenger has appeared!  The only non-linux computer in the Penguin lab, Waimanu is a dual hex-core Mac running Mac OS X Mountain Lion (10.8.2).

    Apple PowerMac
    2x  Intel Xeon 6-Core CPU @2.66 GHz
    ATI Radeon HD 5870
    12GB RAM

Linux Lab 01 through 06 - Dell
    6x  Dell Optiplex GX520
    Intel Pentium D 2-Core CPU @2.80 GHz
    3.5GB RAM

Linux 13 through 18 - Lenovo
    6x  Lenovo/IBM ThinkCentre
    Intel Pentium 2-Core CPU @1.8 GHz
    4GB RAM

\subsection*{Akeley 203 - Classroom}
    With the processing power to rival that of Cobblepot, each of these machines stouts an impressive (as of 2012) nVidia GeForce GTX 560 graphics card.  While this lab is primarily used as a classroom for networking and graphics classes, we hope to one day harness the power of these 33 machines as a LuxRender or CUDA cluster, but for now, they'll remain as thunclients for the poor souls using the Windows virtual machines.

    33x Custom Built by Voyageur
    Intel Core i5-2400 4-Core @3.10 GHz
    nVidia GeForce GTX 560
        336 General Purpose GPU Cores @1.620 GHz
        1GB Dedicated Memory
    8GB RAM
